MSDS 6306: Doing Data Science - Case Study 01 - Beers/Breweries Dataset

### 2020-10-14 MSDS6306_DDS_CaseStudy01-Beersdataset.Rmd
Rmd File

# ABV statistical attributes
```{r}
Stats <- Totaldata %>% summarize(Mean = mean(ABV, na.rm=TRUE),
                        Median = median(ABV,na.rm=T), Max = max(ABV,na.rm=T), Min = min(ABV,na.rm=T),
                        SD = sd(ABV,na.rm=T), N = n())
#Histogram and Density Plot
His_Den <- Totaldata %>% filter(!is.na(ABV)) %>% ggplot(aes(x=ABV)) +
  geom_histogram(aes(y=..density..),colour='red',fill='blue', binwidth = 0.0035) +
  geom_density(alpha=.4, fill='#FFFF00') + 
  ggtitle('ABV Statistical Attributes - Histogram, Density and Box Plots') + 
  scale_x_continuous(expand = c(0,0), limit = c(0,0.14)) + labs(y="Density / Count")

@@

>>>>

# ABV statistical attributes
```{r ABV statistical attributes}
Stats <- Totaldata %>% summarize(Mean = mean(ABV, na.rm=TRUE),
                        Median = median(ABV,na.rm=T), Max = max(ABV,na.rm=T), Min = min(ABV,na.rm=T),
                        SD = sd(ABV,na.rm=T), N = n())
#Histogram and Density Plot
His_Den <- Totaldata %>% filter(!is.na(ABV)) %>% ggplot(aes(x=ABV)) +
  geom_histogram(aes(y=..density..),colour='red',fill='blue', binwidth = 0.0035) +
  geom_density(alpha=.4, fill='#FFFF00') + 
  ggtitle('ABV Statistical Attributes - Histogram, Density and Box Plots') + 
  scale_x_continuous(expand = c(0,0), limit = c(0,0.14)) + labs(y="Density / Count")

@@

# ABV v. IBU scatter plot
```{r ABV v. IBU}
#Scatter plot with 
Totaldata %>% filter(!is.na(ABV) & !is.na(IBU)) %>% 
  ggplot(aes(y=ABV, x=IBU)) + geom_point(aes(colour = ABV/IBU)) + geom_smooth(method=loess) + ggtitle("ABV V. IBU Plot") + scale_y_continuous(labels = percent)
